Learning Heuristics of SAT by Graph Neural Networks

### 2018-12-15 report/paper.tex
update

Table 1 shows the basic statistical information (number of decisions) of 50 testing instances.
As we can see, compared with randomly picking a variable, 
the naive linear embedding already improves the performance.
However, we observe decline when using the graph neural network -- it has roughly the same
performance with the random stategy according the average stesp.

Figure 1 provides a detailed comparision between the three models based on the residual 
steps of these 50 test instances. In the graph noted in the form of "A vs. B", we obtain
the residual steps by computing $steps(B) - steps(A)$ for each instances.
For example, Figure 1 (a) shows the comparision between random strategy and RL with linear 
embedding, the negative numbers on y-axis mean that on these instances the RL model performs
better than the random strategy -- overall, RL is better on 52\% instances.
If we compare the random baseline with graph-based RL, again, we do not observe
significant improvement. We conjuecture this happens from two reasons: 
1) the graph model although captures the structural information, but it is more 
sophisticated, further parameter tunning (as well as for the policy network) 
may improve the performance;
2) If the model is trained with more data, we can expect a performance imporvement.

@@

As artifical neural networks greatly succeeded in vision and natural language tasks in last ten years,
many works that combine deep learning and logical reasoning also has been emerged recently.
Some of the work are completely based on neural network, as opposed to utilizing
an existing deterministic framework. \citeauthor{selsam2018learning} proposed to 
use message-passing neural network to learn the assignment of a SAT problem \cite{selsam2018learning}.
We adapt a similar graph representation from \citeauthor{selsam2018learning}, but use it 
on DPLL, which poses a difficulty on handling dynamic graph strcuture.
Based on \citeauthor{selsam2018learning}'s NeuraSAT, a ICLR 2019 paper
further improves the model that directly generates the assignment in a unsupervised fashion, 
but works on circuit-sat problem\cite{anonymous2019learning}.

@@

We investigate the problem of learning branching heuristics of SAT by 
graph neural networks and show the preliminary result. 
We note that since the random 3-SAT problems are not tightly constrained,
which means there may exist many satisfiable assignments, the numbers we showed
in Section 4 does not strictly imply the policy network has learned effective
branching heuristics. We leave the examination of ability of generalizing
on larger instances as future works. The graph currently experimented is still 
static, implementing and tweaking the dynamicaly updated GNN (as discussed in 
Section 2.2) is another on-going work.

>>>>

Table 1 shows the basic statistical information (number of decisions) of 50 testing instances.
As we can see, compared with randomly picking a variable, 
the naive linear embedding already improves the performance.
However, we observe decline when using the graph neural network -- it has roughly the same
performance with the random strategy according the average steps.

Figure 1 provides a detailed comparison between the three models based on the residual 
steps of these 50 test instances. In the graph noted in the form of "A vs. B", we obtain
the residual steps by computing $steps(B) - steps(A)$ for each instances.
For example, Figure 1 (a) shows the comparison between random strategy and RL with linear 
embedding, the negative numbers on y-axis mean that on these instances the RL model performs
better than the random strategy -- overall, RL is better on 52\% instances.
If we compare the random baseline with graph-based RL, again, we do not observe
significant improvement. We conjecture this happens from two reasons: 
1) the graph model although captures the structural information, but it is more 
sophisticated, further parameter tunning (as well as for the policy network) 
may improve the performance;
2) If the model is trained with more data, we can expect a performance improvement.

@@

As artificial neural networks greatly succeeded in vision and natural language tasks in last ten years,
many works that combine deep learning and logical reasoning also has been emerged recently.
Some of the work are completely based on neural network, as opposed to utilizing
an existing deterministic framework. \citeauthor{selsam2018learning} proposed to 
use message-passing neural network to learn the assignment of a SAT problem \cite{selsam2018learning}.
We adapt a similar graph representation from \citeauthor{selsam2018learning}, but use it 
on DPLL, which poses a difficulty on handling dynamic graph structure.
Based on \citeauthor{selsam2018learning}'s NeuraSAT, a ICLR 2019 paper
further improves the model that directly generates the assignment in a unsupervised fashion, 
but works on circuit-sat problem\cite{anonymous2019learning}.

@@

We investigate the problem of learning branching heuristics of SAT by 
graph neural networks and show the preliminary result. 
We note that since the random 3-SAT problems are not tightly constrained,
which means there may exist many satisfiable assignments, the numbers we showed
in Section 4 does not strictly imply the policy network has learned effective
branching heuristics. We leave the examination of ability of generalizing
on larger instances as future works. The graph currently experimented is still 
static, implementing and tweaking the dynamically updated GNN (as discussed in 
Section 2.2) is another on-going work.
